### 2018-09-07 manuscript.tex
Update manuscript.tex

@@

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.

@@

>>>>

Baseline socio-demographic and sample characteristics are shown in xxx.

@@

--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on "coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

@@

\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
